Supplemental Appendix for ``Out-of-Sample Comparisons of Overfit Models''

### 2016-03-09 appendix.tex
[#51] Switch BibTeX database to latex-tools version
This switch adds records for a few papers and (probably more important)
updates the records of a few of my papers in the BibTeX database. The
bibtex keys change for those papers, so the files need to be updated
in the LaTeX files as well.
[#49] Add code to generate and import Git info into LaTeX files
This commit adds code to the makefile to generate a (short) new file VERSION.tex
with information on the repository version (if the commit is tagged) or commit.
That imformation is included as the date and header of the final pdfs.
Include appen

\documentclass[12pt]{article}
\input{setup}

\title{Supplamental Appendix for ``Out-of-Sample Comparisons of
  Overfit Models''}
\author{Gray Calhoun\thanks{email: \protect\url{gcalhoun@iastate.edu}} \\
  Iowa State University}

@@

This appendix presents simulation results that accompany
\cite{Cal:14}. As in the main paper, these simulations were conducted
in R \citep{Rde:10} using the MASS \citep{VeR:02}, Matrix
\citep{BM:13}, rlecuyer \citep{SR:12}, and RSQLite \citep{Jam:10}
packages. Graphs were produced in R using Lattice \citep{Sar:10} and
tikzDevice \citep{ShB:11:0.6.1}.

\nocite{DiM:95,Wes:96,Mcc:07,ClW:06,ClW:07}
\bibliographystyle{abbrvnat}
\bibliography{references}

\begin{figure}\centering
  {\large Coverage of recursive DMW OOS interval in simulations}
  \input{floats/mc-interval-generror1-rec.tex}
  \caption{Simulated coverage of $\E_T \oosB$ at 90\% confidence using
    a one-sided interval based on the recursive DMW \oost\ test,
    plotted as a function of the fraction of observations used in the
    test sample, $P/T$.  The solid horizontal line denotes the
    intervals' nominal coverage.}
  \label{fig:interval-T}
\end{figure}

\begin{figure}\centering
  {\large Size of recursive DMW \oost\ test in simulations}
  \input{floats/mc-dmwsize-rec.tex}
  \caption{Simulated rejection probabilities for the recursive DMW
    \oost\ test under the null hypothesis that the benchmark model is
    more accurate, $\E_T \oosB \leq 0$. Nominal size is 10\% and is
    marked with a solid horizontal line. Values greater than 10\%
    indicate that the test rejects the benchmark model too often.}
  \label{fig:ttest-size}
\end{figure}

\begin{figure}\centering
  {\large Size of recursive Clark-West OOS test in simulations}
  \input{floats/mc-clarkwestsize-rec.tex}
  \caption{Simulated rejection probabilities for Clark and West's
    (2006, 2007) recursive OOS test statistic under the null
    hypothesis that the benchmark model is more accurate, $\E_T \oosB
    \leq 0$. Nominal size is 10\% and is marked with a solid
    horizontal line. Values greater than 10\% indicate that the test
    rejects the benchmark model too often.}
  \label{fig:clarkwest}
\end{figure}

\begin{figure}\centering
  {\large Size of recursive McCracken \oost\ test in simulations}
  \input{floats/mc-mccrackensize-rec.tex}
  \caption{Simulated rejection probabilities for McCracken's (2007)
    recursive \oost\ test under the null hypothesis that the benchmark
    model is more accurate, $\E_T \oosB \leq 0$. Nominal size is 10\%
    and is marked with a solid horizontal line. Values greater than
    10\% indicate that the test rejects the benchmark model too
    often.}
  \label{fig:mccracken}
\end{figure}

\begin{figure}\centering
  {\large Power of recursive DMW \oost\ test in simulations}
  \input{floats/mc-dmwpower-rec.tex}
  \caption{Simulated rejection probabilities for the recursive DMW
    \oost\ test under the alternative that the benchmark model is less
    accurate, $\E_T \oosB > 0$. Nominal size is 10\% and is marked
    with a solid horizontal line. Values greater than 10\% indicate
    that the test rejects the benchmark model too often.}
  \label{fig:ttest-power}
\end{figure}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "appendix"
%%% End:

>>>>

\documentclass[12pt,draft]{article}
\input{setup}

\title{Supplemental Appendix for ``Out-of-Sample Comparisons of
  Overfit Models''}
\author{Gray Calhoun\thanks{email: \protect\url{gcalhoun@iastate.edu}} \\
  Iowa State University}

\date{\VERSION}

@@

\input{appendix_contents.tex}

\bibliographystyle{abbrvnat}
\bibliography{latex-tools-0.2.1/references}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "appendix.tex"
%%% TeX-command-extra-options: "-shell-escape"
%%% End:
